Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-05 paper/paper.tex
update

\subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.
In all the examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices;
the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$.

@@

\begin{figure}[t] 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
    \caption{Square square entropy constants for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $1000$.}
    \label{fig:lattices}
\end{figure}

\subsubsection{Number of independent sets and hard-square entropy constant}
The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.

>>>>

\subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.

\subsubsection{Number of independent sets and hard-square entropy constant}
In this examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices;
the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$. 
The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
We computed the integer sequences for $L=38$ and $L=39$, which is not known before to our knowledge.
In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
We also computed hard square entropies for these lattices and shown the results in \Fig{fig:hardsquare}.

@@

\begin{figure}[t] 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
    \caption{Hard square entropy for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $100$.}
    \label{fig:hardsquare}
\end{figure}
